---
title: "statCalc"
runtime: shiny
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Stat Calculator for Marketing Research

This presentation shows the features of a statistical calculator made for marketing research.  A wide variety of marketing research tasks rely on statistical inference.

Three such areas covered by this calculator's functionality are:

* Sample Size Computation
* A/B Testing
* Margin of Error Computation

The following slides will demo the pages of the calculator.  Please feel free to play with the calculation inputs as the pages are interactive.
Formulas for the calculations are on the bottom of each slide.

This view the calculator on the web, please visit: https://collier.shinyapps.io/Shiny_StatCalculator/

## Sample Size Computation

```{r SampleSize}
library(shiny)

shinyApp (
  shinyUI(
    navbarPage("Stat Calculator for Marketing Research",
               tabPanel("Sample Size", uiOutput('page1'))
    )
  ),
  
  shinyServer(function(input, output, session) {
    
    
    output$page1 <- renderUI({
      sidebarLayout(
        sidebarPanel(
          tags$head( tags$script(src="http://cdn.mathjax.org/mathjax/latest/MathJax.js?config=TeX-AMS_HTML-full", type = 'text/javascript'),
                     tags$script( "MathJax.Hub.Config({tex2jax: {inlineMath: [['$','$'], ['\\(','\\)']]}});", type='text/x-mathjax-config')),
          radioButtons("radio", label = h3("Compute Sample Size Needed For:"),
                       choices = list("A - Estimation of Sample Proportion - Discrete Variable" = 1, 
                                      "B - Estimation of Sample Mean - Continuous Variable" = 2)),
          
          numericInput("num1", label = h5("Enter Desired Margin of Error $$ \\large\\ e $$"), value = .05),
          
          numericInput("num2", label = h5("Enter Population Standard Deviation $$ \\large\\sigma $$"), value = 100)
          
          
        ),
        mainPanel(
            
            withMathJax(helpText("Formula A - Use when e is a percentage, ex: 5% $$ \\large\\ n=\\frac{1}{e^2}$$ Formula B - Use when e is a continuous variable, ex: 100 $$ \\large\\ n=\\frac{4*\\sigma^2}{e^2}$$")),
            
          output$text2 <- renderText({
            "Sample Size:"
          }),
          
          output$value4646 <- renderPrint({
            if ((input$radio==1)){
              
              
              1/(input$num1^2)
              # "Sample Size Formula (: $$ \\Huge\\frac{1}{e^2}$$"
              
            } else { 
              4*(input$num2^2)/(input$num1^2)
              
            }
          })
            )
        )
      
    })

    
    })
)
```

## A/B Testing

```{r A/B testing}
library(shiny)

shinyApp (
  shinyUI(
    navbarPage("Stat Calculator for Marketing Research",
               tabPanel("A/B Testing", uiOutput('page2'))
    )
  ),
  
  shinyServer(function(input, output, session) {
    
    
    #Page 2
    output$page2 <- renderUI({
      
      fixedRow(
        column(9,
               "",
               fixedRow(
                 column(3,
                        "",
                        numericInput("numCP",label = h5("Control Population"),value=1000),
                        numericInput("numCR",label = h5("Control Response"),value=100),
                        
                        # output$text999999999 <- renderText({
                        #         
                        #         "test"
                        #         
                        # }),
                        
                        output$valueYLD979984 <- renderPrint({
                          
                          input$numCR/input$numCP
                          
                        })
                 ),
                 column(3,
                        "",
                        numericInput("testCP",label=h5("Test Population"),value=1000),
                        numericInput("testCR",label=h5("Test Response"),value=100),
                        
                        output$Value28433311143 <- renderPrint({
                          
                          input$testCR/input$testCP
                        })
                        
                 ),
                 column(5, offset = 1,
                        "Group Superiority:",
                        output$Value341762342467 <- renderPrint({
                          if (input$numCR/input$numCP == input$testCR/input$testCP){
                            'Equal'
                          } else if (input$numCR/input$numCP > input$testCR/input$testCP){
                            'Control Group'
                          } else {
                            'Test Group'
                          }
                        })
                 ),
                 column(5,
                        "Lift Percent:", offset = 1,
                        output$Value4416871467 <- renderPrint({
                          ((input$testCR/input$testCP) - (input$numCR/input$numCP))/ (input$numCR/input$numCP)
                        })
                 ),
                 
                 column(5,
                        "Z-Score:", offset = 1,
                 
                 output$value87292 <- renderPrint({
                   
                   cntPop <- input$numCP
                   cntRsp <- input$numCR
                   cntYld <- cntRsp/cntPop
                   tstPop <- input$testCP
                   tstRsp <- input$testCR
                   tstYld <- tstRsp/tstPop
                   
                   stdErrorControl <- sqrt(((cntRsp/cntPop)*(1-(cntRsp/cntPop))/cntPop))
                   stdErrorTest <- sqrt(((tstRsp/tstPop)*(1-(tstRsp/tstPop))/tstPop))
                   zScore <- (cntYld - tstYld)/sqrt((stdErrorControl^2)+(stdErrorTest^2))
                   
                   zScore
                   
                 }),
                 
                 column(9,
                        "P value:",
                        
                        output$value454643114 <- renderPrint({
                          
                          cntPop <- input$numCP
                          cntRsp <- input$numCR
                          cntYld <- cntRsp/cntPop
                          tstPop <- input$testCP
                          tstRsp <- input$testCR
                          tstYld <- tstRsp/tstPop
                          
                          stdErrorControl <- sqrt(((cntRsp/cntPop)*(1-(cntRsp/cntPop))/cntPop))
                          stdErrorTest <- sqrt(((tstRsp/tstPop)*(1-(tstRsp/tstPop))/tstPop))
                          zScore <- (cntYld - tstYld)/sqrt((stdErrorControl^2)+(stdErrorTest^2))
                          pVal <- pnorm(zScore)
                          
                          pVal
                          
                        })
                 ),
                 column(7,
                        "90% Confidence Level:",
                        output$value21131313 <- renderPrint({
                          cntPop <- input$numCP
                          cntRsp <- input$numCR
                          cntYld <- cntRsp/cntPop
                          tstPop <- input$testCP
                          tstRsp <- input$testCR
                          tstYld <- tstRsp/tstPop
                          
                          stdErrorControl <- sqrt(((cntRsp/cntPop)*(1-(cntRsp/cntPop))/cntPop))
                          stdErrorTest <- sqrt(((tstRsp/tstPop)*(1-(tstRsp/tstPop))/tstPop))
                          zScore <- (cntYld - tstYld)/sqrt((stdErrorControl^2)+(stdErrorTest^2))
                          pVal <- pnorm(zScore)
                          if (pVal > .9 | pVal < .1){
                            "TRUE"
                          }
                        })
                 ),
                 column(7,
                        "95% Confidence Level:",
                        output$value36161616 <- renderPrint({
                          cntPop <- input$numCP
                          cntRsp <- input$numCR
                          cntYld <- cntRsp/cntPop
                          tstPop <- input$testCP
                          tstRsp <- input$testCR
                          tstYld <- tstRsp/tstPop
                          
                          stdErrorControl <- sqrt(((cntRsp/cntPop)*(1-(cntRsp/cntPop))/cntPop))
                          stdErrorTest <- sqrt(((tstRsp/tstPop)*(1-(tstRsp/tstPop))/tstPop))
                          zScore <- (cntYld - tstYld)/sqrt((stdErrorControl^2)+(stdErrorTest^2))
                          pVal <- pnorm(zScore)
                          if (pVal > .95 | pVal < .05){
                            "TRUE"
                          }
                        })
                 ),
                 column(7,
                        "99% Confidence Level:",
                        output$value46446710 <- renderPrint({
                          cntPop <- input$numCP
                          cntRsp <- input$numCR
                          cntYld <- cntRsp/cntPop
                          tstPop <- input$testCP
                          tstRsp <- input$testCR
                          tstYld <- tstRsp/tstPop
                          
                          stdErrorControl <- sqrt(((cntRsp/cntPop)*(1-(cntRsp/cntPop))/cntPop))
                          stdErrorTest <- sqrt(((tstRsp/tstPop)*(1-(tstRsp/tstPop))/tstPop))
                          zScore <- (cntYld - tstYld)/sqrt((stdErrorControl^2)+(stdErrorTest^2))
                          pVal <- pnorm(zScore)
                          if (pVal > .99 | pVal < .01){
                            "TRUE"
                          }
                        }))
                 
                 
               )
        ),
        column(12,
               "",
               fixedRow(
                 column(6,
                        withMathJax(helpText("Standard Error Formula Control Group $$\\large\\ SE_c = \\sqrt{\\frac{Resp_c}{Resp_t}*(1-\\frac{Yield_c}{Pop_c})}$$")),
                        
                        
                        withMathJax(helpText("Z-Score Formula $$\\large\\ Z = \\frac{Yield_c - Yield_t}{\\sqrt{(SE_c^2+SE_t^2)}}$$"))
                        
                        
                 ),
                 
                 column(6,
                        withMathJax(helpText("Standard Error Formula Test Group $$\\large\\ SE_t = \\sqrt{\\frac{Resp_t}{Resp_c}*(1-\\frac{Yield_t}{Pop_t})}$$")),
                        
                        
                        withMathJax(helpText("P-Value calculated with R function pnorm on Z-Score value"))
                        
                 )
               )
               
        )
      )
      )
      
    })

    })
)
```

## Margin of Error Computation

```{r Margin of Error}
library(shiny)

shinyApp (
  shinyUI(
    navbarPage("Stat Calculator for Marketing Research",
               tabPanel("Margin of Error", uiOutput('page3'))
    )
  ),
  
  shinyServer(function(input, output, session) {
    
    

    output$page3 <- renderUI({
      
      fixedRow(
        column(9,
               "",
               fixedRow(
                 column(5,
                        "Estimation of a Sample Proportion",
                        numericInput("sampSize1",label = h5("Sample Size"),value = 1000),
                        numericInput("sampResp1", label= h5("Sample Response"), value = 100),
                        
                        
                        output$text4599898985 <- renderText({
                          "Sample Proportion:"
                        }),
                        
                        output$valueSP4245 <- renderPrint({
                          input$sampResp1/input$sampSize1
                        }),
                        
                        output$text244645 <- renderText({
                          "Standard Error of Sample Proportion:"
                          
                        }),
                        
                        output$valueSE45245 <- renderPrint({
                          
                          sqrt((input$sampResp1/input$sampSize1)*(1-((input$sampResp1/input$sampSize1)))/input$sampSize1)
                          
                          
                        }),
                        
                        
                        output$text34245 <- renderText({
                          "Standard Error 95% CI: Lower:"
                          
                        }),
                        
                        output$valueCI4254 <- renderPrint({
                          
                          (input$sampResp1/input$sampSize1) - (1.95*(sqrt((input$sampResp1/input$sampSize1)*(1-((input$sampResp1/input$sampSize1)))/input$sampSize1)))
                          
                        }),
                        
                        
                        output$text3785272 <- renderText({
                          "Standard Error 95% CI: Upper:"
                          
                        }),
                        
                        output$valueCI42547 <- renderPrint({
                          
                          (input$sampResp1/input$sampSize1) + (1.95*(sqrt((input$sampResp1/input$sampSize1)*(1-((input$sampResp1/input$sampSize1)))/input$sampSize1)))
                          
                        }),
                        
                        
                        output$text452727 <- renderText({
                          
                          "Margin of Error"
                          
                          
                        }),
                        
                        output$me27272744 <- renderPrint({
                          
                          ((input$sampResp1/input$sampSize1) + (1.95*(sqrt((input$sampResp1/input$sampSize1)*(1-((input$sampResp1/input$sampSize1)))/input$sampSize1)))) - (input$sampResp1/input$sampSize1)
                          
                        }),
                        
                        
                        withMathJax(helpText("Standard Error of Sample Proportion Formula $$\\large\\ SE(\\hat{p}) = \\sqrt{\\frac{\\hat{p}*(1-\\hat{p})}{n}}$$")),
                        
                        withMathJax(helpText("95% Confidence Interval of Sample Proportion Formula $$\\large\\ (\\hat{p} - (1.96 * \\hat{p}),   \\hat{p} + (1.96 * \\hat{p}))  $$"))
                        
                 ),
                 column(5, offset=2,
                        "Estimation of a Sample Mean",
                        numericInput("sampSize2",label = h5("Sample Size"),value = 1000),
                        numericInput("sampMean", label= h5("Sample Mean"), value = 2),
                        numericInput("sampSD", label = h5("Sample Standard Deviation"),value=0.5),
                        
                        output$text4888889 <- renderText({
                          
                          "Standard Error of Sample Mean"
                          
                        }),
                        
                        output$ValueSE298983 <- renderPrint({
                          
                          input$sampSD/(sqrt(input$sampSize2))
                          
                        }),
                        
                        output$text3213538 <- renderText({
                          "Standard Error 95% CI: Lower:"
                          
                        }),
                        
                        output$valueCI118984 <- renderPrint({
                          
                          input$sampMean - (1.96*(input$sampSD/(sqrt(input$sampSize2))))
                          
                        }),
                        
                        
                        output$text331618 <- renderText({
                          "Standard Error 95% CI: Upper:"
                          
                        }),
                        
                        output$valueCI224649 <- renderPrint({
                          
                          input$sampMean + (1.96*(input$sampSD/(sqrt(input$sampSize2))))
                          
                        }),
                        
                        output$text4198719 <- renderText({
                          
                          "Margin of Error"
                          
                          
                        }),
                        
                        output$me1989883 <- renderPrint({
                          
                          ((input$sampMean + (1.96*(input$sampSD/(sqrt(input$sampSize2))))) - input$sampMean)
                        }),
                        
                        withMathJax(helpText("Standard Error of Sample Mean Formula $$\\large\\ SE(\\bar X) = \\frac{\\sigma}{\\sqrt{n}} $$")),
                        
                        withMathJax(helpText("95% Confidence Interval of Sample Proportion Formula $$\\large\\ (\\bar X - (1.96 * \\bar X),   \\bar X + (1.96 * \\bar X))  $$"))
                        
                 )
               )
        )
      )
      
    })
    
    
    
    })
)
```

